### 2011-07-31 doc/theses/svirec/kap5.tex
added section about jInfer and some DTDs to the experimental part.

@@

The main part of our algorithm is implemented as the \texttt{FDRepairer} extension of the jInfer framework. The core package of the extension is \texttt{cz.cuni.mff.\discretionary{}{}{}ksi.jinfer.functionalDependencies} and contains classes representing base object important for repairing (Tuple, RW-XML tree, Path etc.). This package is further divided into the following subpackages:

@@

The \texttt{FDRepairer} extension of the jInfer framework is an implementation of our proposed algorithm presented in Chapter \ref{kap4}. However, one part of the algorithm have not been implemented yet, namely the intersection of repair candidates with existing repair group.

>>>>

\section{jInfer Framework}

jInfer framework was developed as a Software Project at the Faculty of Mathematics and Physics, Charles University at Prague. The framework is based on NetBeans platform and is mainly used for XML schema inference. Although our proposed algorithm is not dealing with the schema inference, jInfer is designed to be extensible and is suitable for incorporation our algorithm into it.

The whole process of repairing inconsistent XML data is divided three steps (illustrated in Fig. \ref{repairProcess}):

\begin{enumerate}
	\item Import of input data (XML, functional dependencies, weights) into an internal representation - \emph{Initial Model}.
    \item Repairing of \emph{Initial Model} with optional help of user interaction.
    \item Export back the repaired data into XML format.
\end{enumerate}

\begin{figure}[H]
    \centering\includegraphics[width=0.6\textwidth]{repair_process}
    \caption{High-level view of the repair process}
    \label{repairProcess}
\end{figure}

@@

The main part of our algorithm is implemented as the \texttt{FDRepairer} module of the jInfer framework. The core package of the module is \texttt{cz.cuni.mff.\discretionary{}{}{}ksi.jinfer.functionalDependencies} and contains classes representing base object important for repairing (Tuple, RW-XML tree, Path etc.). This package is further divided into the following subpackages:

@@

The \texttt{FDRepairer} module of the jInfer framework is an implementation of our proposed algorithm presented in Chapter \ref{kap4}. However, one part of the algorithm have not been implemented yet, namely the intersection of repair candidates with existing repair group.
